Plant-pollintor networks worldwide are composed by the same specific building blocks

### 2021-05-18 Draft/Draft.Rmd
Minimal edits + Fig 2 do not work

---
title: "Plant-pollintor networks worldwide are composed by the same specific building blocks"
output: html_document
---

@@

1) over and under represented motifs
```{r}
library(lme4)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
str(d)
head(d)

@@

ggplot(NULL) + 
  geom_point(data = d %>% filter(motif != 1),
             aes(x=as.factor(motif), y=percentil_sizeclass, 
                 color = as.factor(motif)),
             position = "jitter",alpha=0.5)+
  geom_errorbar(data = motif_means,aes(x = as.factor(motif), ymin=mean-SE, ymax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = motif_means,aes(x = as.factor(motif), y=mean), 
                size=2)+
  labs(x="Motif", y = "Percentile")+
  theme_bw()+
  theme(legend.position = "none")

#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
```
2) FG-position associations.
```{r}
library(lme4)
library(tidyverse)
library(stringi)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

plant_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
         !is.na(expected_freq_its_GF))
pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
         !is.na(expected_freq_its_GF))

>>>>

---
title: "Plant-pollintor networks worldwide are composed by the same specific building blocks"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

1) over and under represented motifs
```{r}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
str(d)
head(d)

@@

ggplot(NULL) + 
  geom_point(data = d %>% filter(motif != 1),
             aes(y=as.factor(motif), x=percentil_sizeclass, 
                 color = as.factor(motif)),
             position = "jitter",alpha=0.5)+
  geom_errorbar(data = motif_means,aes(y = as.factor(motif), xmin=mean-SE, xmax=mean+SE), 
                width=1.0,size=1)+
  geom_point(data = motif_means,aes(y = as.factor(motif), x=mean), 
                size=2)+
  labs(y="Motif", x = "Percentile")+
  theme_bw()+
  theme(legend.position = "none")

#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
#NICE! Can we put motifs in Y axes, and % in X?
```
2) FG-position associations.
```{r}
library(lme4)
library(nlme)
library(tidyverse)
library(stringi)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

plant_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(Node_FG %in% list_plants_FG, !position %in% c(1,2),
         !is.na(expected_freq_its_GF)) #ME DA ERROR
pollinator_position_percentiles_filtered <- all_position_percentiles %>% 
  filter(!Node_FG %in% list_plants_FG, !position %in% c(1,2),
         !is.na(expected_freq_its_GF))
